Analysis-ready VCF at Biobank scale using Zarr

### 2025-04-01 paper.tex
Make second author bucket
Fix up affils

%%% Use the \authfn to add symbols for additional footnotes, if any.
% 1 is reserved for correspondence emails; then continuing with 2 etc for contributions.
% First author
\author[1,2\authfn{1}]{Eric Czech} % https://orcid.org/0000-0002-4254-4255
\author[3,4\authfn{1}]{Timothy R. Millar} % https://orcid.org/0000-0002-5142-8811
\author[5,\authfn{1}]{Will Tyler}
\author[6,\authfn{1}]{Tom White}

% Middle, alphabetical order
\author[7]{Benjamin Elsworth} % https://orcid.org/0000-0001-7328-4233
\author[8,9]{Jérémy Guez} % https://orcid.org/0009-0007-6406-5187
\author[10]{Jonny Hancox} % https://orcid.org/0009-0003-5799-5299
\author[11]{Ben Jeffery} % https://orcid.org/0000-0002-1982-6801
\author[8,9,12]{ Konrad J. Karczewski} % https://orcid.org/0000-0003-2878-4671
\author[13]{Alistair Miles} % https://orcid.org/0000-0001-9018-4680
\author[14]{Sam Tallman} % https://orcid.org/0000-0001-7183-6276
\author[15]{Per Unneberg} % https://orcid.org/0000-0001-5735-3315
\author[1]{Rafal Wojdyla} % https://orcid.org/0009-0005-0735-7090
\author[16]{Shadi Zabad} % https://orcid.org/0000-0002-8003-9284

% Senior
\author[1,2,\authfn{2}]{Jeff Hammerbacher} % https://orcid.org/0000-0001-6596-8563
\author[11,\authfn{2},\authfn{3}]{Jerome Kelleher} % https://orcid.org/0000-0002-7894-5253

\affil[1]{Open Athena AI Foundation}
\affil[2]{Related Sciences}
\affil[3]{The New Zealand Institute for Plant \& Food Research Ltd, Lincoln,
New Zealand}
\affil[4]{Department of Biochemistry, School of Biomedical Sciences, University of Otago, Dunedin, New Zealand}
\affil[5]{Independent researcher}
\affil[6]{Tom White Consulting Ltd.}
\affil[7]{Our Future Health, Manchester, UK.}
\affil[8]{Program in Medical and Population Genetics, Broad Institute of MIT and Harvard, Cambridge, Massachusetts 02142, USA}
\affil[9]{Analytic and Translational Genetics Unit, Massachusetts General
Hospital, Boston, Massachusetts 02114, USA}
\affil[10]{NVIDIA Ltd, Reading, UK}
\affil[11]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
University of Oxford, UK}
\affil[12]{Novo Nordisk Foundation Center for Genomic Mechanisms of Disease, Broad Institute of MIT and Harvard, Cambridge, Massachusetts 02142, USA}
\affil[13]{Wellcome Sanger Institute}
\affil[14]{Genomics England}
\affil[15]{Department of Cell and Molecular Biology, National
  Bioinformatics Infrastructure Sweden, Science for Life Laboratory,
  Uppsala University, Uppsala, Sweden}
\affil[16]{School of Computer Science, McGill University, Montreal, QC, Canada}

%%% Author Notes
\authnote{\authfn{1}Joint first author.}
\authnote{\authfn{2}Joint senior author.}
\authnote{\authfn{3}jerome.kelleher@bdi.ox.ac.uk}

>>>>

%%% Use the \authfn to add symbols for additional footnotes, if any.
% 1 is reserved for correspondence emails; then continuing with 2 etc for contributions.
% First author
\author[1,2\authfn{1}]{Eric Czech} % https://orcid.org/0000-0002-4254-4255
\author[3,\authfn{1}]{Will Tyler}
\author[4,\authfn{1}]{Tom White}

\author[5\authfn{2}]{Ben Jeffery} % https://orcid.org/0000-0002-1982-6801
\author[6,7\authfn{2}]{Timothy R. Millar} % https://orcid.org/0000-0002-5142-8811

% Middle, alphabetical order
\author[8]{Benjamin Elsworth} % https://orcid.org/0000-0001-7328-4233
\author[9,10]{Jérémy Guez} % https://orcid.org/0009-0007-6406-5187
\author[11]{Jonny Hancox} % https://orcid.org/0009-0003-5799-5299
\author[9,10,12]{ Konrad J. Karczewski} % https://orcid.org/0000-0003-2878-4671
\author[13]{Alistair Miles} % https://orcid.org/0000-0001-9018-4680
\author[14]{Sam Tallman} % https://orcid.org/0000-0001-7183-6276
\author[15]{Per Unneberg} % https://orcid.org/0000-0001-5735-3315
\author[1]{Rafal Wojdyla} % https://orcid.org/0009-0005-0735-7090
\author[16]{Shadi Zabad} % https://orcid.org/0000-0002-8003-9284

% Senior
\author[1,2,\authfn{3}]{Jeff Hammerbacher} % https://orcid.org/0000-0001-6596-8563
\author[5,\authfn{3},\authfn{4}]{Jerome Kelleher} % https://orcid.org/0000-0002-7894-5253

\affil[1]{Open Athena AI Foundation}
\affil[2]{Related Sciences}
\affil[3]{Independent researcher}
\affil[4]{Tom White Consulting Ltd.}
\affil[5]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, University of Oxford, UK}
\affil[6]{The New Zealand Institute for Plant \& Food Research Ltd, Lincoln,
New Zealand}
\affil[7]{Department of Biochemistry, School of Biomedical Sciences, University of Otago, Dunedin, New Zealand}
\affil[8]{Our Future Health, Manchester, UK.}
\affil[9]{Program in Medical and Population Genetics, Broad Institute of MIT and Harvard, Cambridge, Massachusetts 02142, USA}
\affil[10]{Analytic and Translational Genetics Unit, Massachusetts General
Hospital, Boston, Massachusetts 02114, USA}
\affil[11]{NVIDIA Ltd, Reading, UK}

\affil[12]{Novo Nordisk Foundation Center for Genomic Mechanisms of Disease, Broad Institute of MIT and Harvard, Cambridge, Massachusetts 02142, USA}
\affil[13]{Wellcome Sanger Institute}
\affil[14]{Genomics England}
\affil[15]{Department of Cell and Molecular Biology, National
  Bioinformatics Infrastructure Sweden, Science for Life Laboratory,
  Uppsala University, Uppsala, Sweden}
\affil[16]{School of Computer Science, McGill University, Montreal, QC, Canada}

%%% Author Notes
\authnote{\authfn{1}Joint first author.}
\authnote{\authfn{2}Joint second author.}
\authnote{\authfn{3}Joint senior author.}
\authnote{\authfn{4}jerome.kelleher@bdi.ox.ac.uk}
